Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-16 paper/paper.tex
rephrase

In the rest of this paper, we set the constant $R$ to $5$.
This is in accordance with the protocol of \cite{lostanlen2018extended}, who trained a metric learning algorithm on the SOL dataset to search for similar instruments and playing techniques, yet without the intervention of a human subject.
Moreover, note that the value $R=5$ typically reflects the number of virtual panels simultaneously on display in a software environment for computer-assisted orchestration.

>>>>

In the rest of this paper, we set the constant $R$ to $5$.
This is in accordance with the protocol of \cite{lostanlen2018extended}, in which the authors trained a metric learning algorithm on the SOL dataset to search for similar instruments and playing techniques, yet without the intervention of a human subject.
Moreover, note that the value $R=5$ typically reflects the number of virtual panels simultaneously on display in a software environment for computer-assisted orchestration.
